The World Bank, Women, Business and the Law

### 2024-02-20 outputs/paper/paper.qmd
changes to graphs

@@

The reproduced table from the 2020 Survey on Sexual Misconduct at Work outlines the proportions of employees reporting inappropriate sexualized behavior, discriminatory behavior, and sexual assault in their work environments. Notably, the data highlights the heightened vulnerability of individuals in the 25 to 34 age group, where 57% of females report experiencing sexualized behaviors. Within this age group, women are twice as likely as men to face discrimination and three times as likely to experience sexual assault.
```{r}
# Install and load necessary packages if not already installed
 # install.packages("tidyverse")

@@

# Create a sideways stacked bar plot
ggplot(data_long, aes(x = Percentage, y = Group, fill = Category)) +
  geom_bar(stat = "identity", position = "dodge", width = 0.7) +
  scale_fill_manual(values = c("#FF9999", "#FF6666", "#FF3333", "#66B2FF", "#3366FF", "#000099"), name = "Category") +
  labs(title = "Sideways Stacked Bar Plot",
       x = "Percentage",
       y = "Group") +
  theme_minimal() +
  theme(
    axis.text.y = element_text(angle = 0, hjust = 1),
    legend.position = "bottom",
    legend.direction = "horizontal",
    legend.box = "horizontal",
    legend.margin = margin(t = 0, unit = "pt")
)

>>>>

```{r}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: Figure for pay
#| fig-align: center
  library(kableExtra)

@@

The reproduced table from the 2020 Survey on Sexual Misconduct at Work outlines the proportions of employees reporting inappropriate sexualized behavior, discriminatory behavior, and sexual assault in their work environments. Notably, the data highlights the heightened vulnerability of individuals in the 25 to 34 age group, where 57% of females report experiencing sexualized behaviors. Within this age group, women are twice as likely as men to face discrimination and three times as likely to experience sexual assault.
```{r}
#| message: false
#| echo: false
#| warning: false
#| fig-cap: Figure 
#| fig-align: center
# Install and load necessary packages if not already installed
 # install.packages("tidyverse")

@@

# Create a sideways stacked bar plot
ggplot(data_long, aes(x = Percentage, y = Group, fill = Category)) +
  geom_bar(stat = "identity", position = "dodge", width = 0.7) +
  scale_fill_manual(values = c("#FF9999", "#FF6666", "#FF3333", "#66B2FF", "#3366FF", "#000099"), name = "Category") +
  labs(title = "Sideways Stacked Bar Plot",
       x = "Percentage",
       y = "Group") +
  theme_minimal() +
  theme(
    axis.text.y = element_text(angle = 0, hjust = 1),
    legend.position = "bottom",
    legend.direction = "horizontal",
    legend.box = "horizontal",
    legend.margin = margin(t = 0, unit = "pt")
)
```
